A Comparison of Parallel Graph Processing Implementations

### 2017-05-15 papers/publication/paper-pollard.tex
conclusion edits

Overall, the GAP Benchmark Suite was the best-performing system across the given datasets though not the most scalable for the graphs used in this study (at most $2^{22}$ vertices). In addition, GAP is the most recent project and also the most robust in terms of the input graphs accepted. Thus, we recommend graph processing algorithm designers compare their BFS implementations to the Graph500 for BFS, GAP Benchmark Suite for smaller problem sizes or a low number of threads (at most 32), and GraphMat for larger problems with more threads. This is despite the fact that GraphBIG has the best scalability, because even at more than 16 threads the runtime for GraphBIG is still at least one order of magnitude slower than GAP or GraphMat for all sampled algorithms. One last consideration is price: GraphMat requires the Intel compiler collection, which is not free.

Future extensions to this work include providing additional automation, for example, for graph format conversions, which would make the use of our framework even easier. Depending on the granularity of experiments, one can also automatically determine the number of repetitions required to get meaningful timing results in a potentially noisy system environment.

>>>>

Overall, the GAP Benchmark Suite was the best-performing system across the given datasets though not the most scalable for the graphs used in this study (at most $2^{22}$ vertices). In addition, GAP is the most recent project and also the most robust in terms of the input graphs accepted. Thus, we recommend graph processing algorithm designers compare their BFS implementations to the Graph500 for BFS, GAP Benchmark Suite for smaller problem sizes or a low number of threads (at most 32), and GraphMat for larger problems with more threads. This is despite the fact that GraphBIG has the best scalability, because even at more than 16 threads the runtime for GraphBIG is still at least one order of magnitude slower than GAP or GraphMat for all sampled algorithms. Last, but not least, one must consider cost and portability: GraphMat requires the Intel compiler collection, which is not free or universally available for all platforms.
